|

### 2021-09-16 paper.Rmd
move ryan to theory
some more results

<!-- % emotion in political science -->
In this study, I follow recent work in political science inspired by moral psychology. Most relevant for this study, @clifford2019emotional finds that a persuasive emotional frame loading on emotions of anger and disgust increases the perception of an issue as being one of moral conviction [@skitka2020psychology; @wisneski2017moralization]. 
Moral conviction, i.e. the conviction that the handling of an issue touches morality and is about fundamental right or wrong, can be seen as a dimension of attitude strength [@skitka2018attitude]. 
While it is often seen as a binary categorization whether or not an issue is a moral one, there is quite some variation in the extent of moralization within issues [@ryan2014reconsidering] with distinct behavioral consequences, such as an absolute unwillingness to compromise [@ryan2017no] or a tendency to view that issue in absolutist term and to be less likely to be open for information about consequences [@ryan2019actions].

@@

* Emotional framing is an important feature of political communication, and theories such as cognitive appraisal theory [@moors2013appraisal] or affective intelligence theory [@marcus2000affective; @marcus2019applying] provide frameworks for empirical expectaitoins about specific emotions.
* Findings from moral psychology on moralization through disgust.
* Importance of moral conviction for compromise, openness to scientific findings on consequences versus absolutist opposition.
* Of course, people are free to have moral convictions about any issue, but if emotional frames can induce moral conviction, we might have to worry about emotionally framed **mis**information also inducing moral conviction.

@@

After having established that a persuasive, emotionally framed message containing misinformation can influence policy opinion and increase moral conviction, I now report the results of the neutral correction in figure \@ref(fig:neutral-correction).

* the neutral correction is effective for the low emotion misinformation, but not the high emotion misinformation

>>>>

<!-- % emotion in political science -->
In this study, I follow recent work in political science inspired by moral psychology. Most relevant for this study, @clifford2019emotional finds that a persuasive emotional frame loading on emotions of anger and disgust increases the perception of an issue as being one of moral conviction [@skitka2020psychology; @wisneski2017moralization]. 
Moral conviction, i.e. the conviction that the handling of an issue touches morality and is about fundamental right or wrong, can be seen as a dimension of attitude strength [@skitka2018attitude].

@@

* Emotional framing is an important feature of political communication, and theories such as cognitive appraisal theory [@moors2013appraisal] or affective intelligence theory [@marcus2000affective; @marcus2019applying] provide frameworks for empirical expectaitoins about specific emotions.
* Findings from moral psychology on moralization through disgust.
* Importance of moral conviction for compromise, openness to scientific findings on consequences versus absolutist opposition. While it is often seen as a binary categorization whether or not an issue is a moral one, there is quite some variation in the extent of moralization within issues [@ryan2014reconsidering] with distinct behavioral consequences, such as an absolute unwillingness to compromise [@ryan2017no] or a tendency to view that issue in absolutist term and to be less likely to be open for information about consequences [@ryan2019actions]. 
* Of course, people are free to have moral convictions about any issue, but if emotional frames can induce moral conviction, we might have to worry about emotionally framed **mis**information also inducing moral conviction.

@@

After having established that a persuasive, emotionally framed message containing misinformation can influence policy opinion and increase moral conviction, I now report the results of the neutral correction in figure \@ref(fig:neutral-correction). The neutral correction is effective for the low emotion misinformation, but not the high emotion misinformation. The emotional frame of the misinformation therefore moderates the correcion effectiveness. Although weakened, the effects on policy opinion and moral conviction induced by the high emotion misinformation persist after the correction, confirming H2b. Even if the correction significantly moves the factual belief after the high emotion misinformation, there still persists an effect of the misinformation relative to the control group. The correction is therefore not successful in eradicating the misinformation effect, which rejects H2a. In sum, there is no belief echo, but a moderation of the correction effectiveness.
